The 2018 heatwave and its implications on ozone induced damage on vegetation in a subartic climate

### 2020-03-23 VegOzone.tex
Outline.

%% 2-column papers and discussion papers
\documentclass[journal abbreviation, manuscript]{copernicus}

@@

\title{TEXT}

@@

\Author[]{}{}
\Author[]{}{}
\Author[]{}{}

\affil[]{ADDRESS}
\affil[]{ADDRESS}

%% The [] brackets identify the author with the corresponding affiliation. 1, 2, 3, etc. should be inserted.

@@

\correspondence{NAME (EMAIL)}

\runningtitle{TEXT}

\runningauthor{TEXT}

@@

\begin{abstract}
TEXT
\end{abstract}

@@

\introduction  %% \introduction[modified heading if necessary]
TEXT

\section{HEADING}
TEXT

\subsection{HEADING}
TEXT

\subsubsection{HEADING}
TEXT

@@

\codeavailability{TEXT} %% use this section when having only software code available

@@

\codedataavailability{TEXT} %% use this section when having data sets and software code available

@@

\videosupplement{TEXT} %% use this section when having video supplements available

@@

\begin{thebibliography}{}

\bibitem[AUTHOR(YEAR)]{LABEL1}
REFERENCE 1

\bibitem[AUTHOR(YEAR)]{LABEL2}
REFERENCE 2

\end{thebibliography}

%% Since the Copernicus LaTeX package includes the BibTeX style file copernicus.bst,
%% authors experienced with BibTeX only have to include the following two lines:
%%
%% \bibliographystyle{copernicus}
%% \bibliography{example.bib}
%%
%% URLs and DOIs can be entered in your BibTeX file as:
%%
%% URL = {http://www.xyz.org/~jones/idx_g.htm}
%% DOI = {10.5194/xyz}

>>>>

%% 2-column papers and discussion papers
\documentclass[bg, manuscript]{copernicus}

@@

\title{The 2018 heatwave and its implications on ozone induced damage on vegetation in a subartic climate}

@@

\Author[1]{Stefanie}{Falk}
\Author[2]{Ane Victoria}{Vollsnes}
\author[3]{Lisa}{Emberson}
\Author[1]{Frode}{Stordal}

\affil[1]{Department of Geosciences, University of Oslo, Oslo, Norway}
\affil[2]{Department of Biosciences, University of Oslo, Oslo, Norway}
\affil[3]{Department of Environment and Geography, University of York, UK}
%% The [] brackets identify the author with the corresponding affiliation. 1, 2, 3, etc. should be inserted.

@@

\correspondence{Stefanie Falk (stefanie.falk@geo.uio.no)}

\runningtitle{2018 heatwave and implication on ozone induced damage on vegetation in subarctic climate}

\runningauthor{Falk et al.}

@@

\begin{abstract}
  \begin{itemize}
  \item ozone damage
  \item present subarctic climate and conditions
    \begin{itemize}
    \item[$\rightarrow$] midnight sun and 23\,\unit{h} open stomata (biological details will be published in a compaignend paper)
    \item[$\rightarrow$] ozone climatology and spring peak
    \end{itemize}
  \item future climate and conditions
    \begin{itemize}
    \item[$\rightarrow$] increase in heatwaves and dry periodes
    \item[$\rightarrow$] shift in start of growing season (into vincity of ozone spring peak)
    \item[$\rightarrow$] increase in tropospheric background ozone
    \end{itemize}
  \item present day test case 2018 vs 2019 ozone induced damage at NIBIO research station Svanhovd
  \item findings and results 
  \end{itemize}
\end{abstract}

@@

\introduction  %% \introduction[modified heading if necessary]
\label{sec:intro}
\begin{itemize}
\item ozone in general
\item ozone induced damage in vegetation
\item present subarctic climate and conditions
  \begin{itemize}
  \item[$\rightarrow$] midnight sun and 23\,\unit{h} open stomata (biological details will be published in a compaignend paper)
  \item[$\rightarrow$] ozone climatology and spring peak
  \end{itemize}
\item future climate and conditions
  \begin{itemize}
  \item[$\rightarrow$] increase in heatwaves and dry periodes
  \item[$\rightarrow$] shift in start of growing season (into vincity of ozone spring peak)
  \item[$\rightarrow$] increase in tropospheric background ozone
  \end{itemize}
\end{itemize}

\section{Data}
TEXT

\subsection{NIBIO research station Svanhovd}
TEXT

\subsection{Other observational data}
TEXT

\subsection{Model and reanalysis data}
TEXT

\section{Statistical analysis}
TEXT

\subsection{Derived climatologies for Svanhovd}
\begin{itemize}
\item temperature
\item precipitation
\item ozone
\end{itemize}

\subsection{2018/19 anomalies}
\begin{itemize}
\item temperature
\item precipitation
\item ozone
\end{itemize}

\section{DO3SE modeling}
Model results for natural and semi-natural vegetation (birch, pine, clover)
\begin{itemize}
\item climatological ozone impact
\item 2018
\item 2019
\end{itemize}

@@

%\codeavailability{TEXT} %% use this section when having only software code available

@@

%\codedataavailability{TEXT} %% use this section when having data sets and software code available

@@

%\videosupplement{TEXT} %% use this section when having video supplements available

@@

%\begin{thebibliography}{}

%\bibitem[AUTHOR(YEAR)]{LABEL1}
%REFERENCE 1

%\bibitem[AUTHOR(YEAR)]{LABEL2}
%REFERENCE 2

%\end{thebibliography}

%% Since the Copernicus LaTeX package includes the BibTeX style file copernicus.bst,
%% authors experienced with BibTeX only have to include the following two lines:
%%
\bibliographystyle{copernicus}
\bibliography{VegOzone.bib}
%%
%% URLs and DOIs can be entered in your BibTeX file as:
%%
%% URL = {http://www.xyz.org/~jones/idx_g.htm}
%% DOI = {10.5194/xyz}
